TAPIR: Threaded Application Programming on Intermittent Resources

### 2017-05-11 paper.tex
Fixed issue with italics, removed trailing whitespace from intro and future notes

\section{Introduction/Background}
  \label{sec:intro}
%A/N: I don't think that the paragraphs in this section are in a great order, but I am having a hard time making it flow better.
%Also I'm absolutely sure each of these paragraphs can definitely be bulked up more for length. Please help thank you!!!
%Also also: I'm trying to get [energy-harvesting computing devices] and [intermittent execution model] below to be in italics,
%but when I use \textit it makes the ENTIRE PAPER in italics, i used the curly braces and everything helpppppp that has never happened to me before

The increase in popularity of Internet of Things (IoT) has led to research focus in wireless technologies and low-power computing.
New technologies in both of these areas has led to new [energy-harvesting computing devices] that operates only with power it has 
collected from the surrounding environment \cite{Chain}. These devices have use cases in medical, IoT, and research applications.

Commonly, an energy-harvesting devices charges and collects power in a storage capacitor until the capacitor reaches a sufficient level of charge.
Once the capacitor is charged, the device begins its operation phase and will run until the capacitor is drained.
This leads to the [intermittent execution model] where regular shut downs and reboots to recharge are the common case rather than the rare case in
a traditional execution model. Because the intermittent execution model includes power failures and reboots, continuous execution programs behave
irregular behavior on an intermittent device and a new programming model is needed.

>>>>

\section{Introduction/Background}
  \label{sec:intro}
%A/N: I don't think that the paragraphs in this section are in a great order, but I am having a hard time making it flow better.
%Also I'm absolutely sure each of these paragraphs can definitely be bulked up more for length. Please help thank you!!!

The increase in popularity of Internet of Things (IoT) has led to research focus in wireless technologies and low-power computing.
New technologies in both of these areas has led to new
\textit{energy-harvesting computing devices} that operates only with power it has
collected from the surrounding environment \cite{Chain}. These devices have use cases in medical, IoT, and research applications.

Commonly, an energy-harvesting devices charges and collects power in a storage capacitor until the capacitor reaches a sufficient level of charge.
Once the capacitor is charged, the device begins its operation phase and will run until the capacitor is drained.
This leads to the \textit{intermittent execution model} where regular shut downs and reboots to recharge are the common case rather than the rare case in
a traditional execution model. Because the intermittent execution model includes power failures and reboots, continuous execution programs behave
irregular behavior on an intermittent device and a new programming model is needed.
